Deliminative verbal reduplication in Mandarin Chinese

### 2024-09-09 replies-reviews.tex

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}\label{verbclass}
First, the notion of ``aspect'' adopted in this article has to be explained in more detail.
We adopt the two-component aspect model proposed by \citet{XiaoMcEnery2004} based on \citet{Smith1991}.
The general term ``aspect'' is considered to encompass the following two components:
situation aspect, i.e. ``aspectual information conveyed by the inherent semantic representation of a verb or an idealized situation'' \citep[21]{XiaoMcEnery2004};
and viewpoint aspect, i.e. ``the aspectual information reflected by the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
Situation aspect can be further modeled as verb classes (dubbed ``Aktionsart'' in the previous version of this paper) at the lexical level
and situation types (the interaction of verb classes and other constituents) at the sentential level \citep[33]{XiaoMcEnery2004}.
The verb classes are determined with verbs in a neutral context (preferably in a perfective viewpoint aspect, with a simple object only when it is obligatory),
where everything that might change the aspectual value of a verb is excluded
and only the inherent features of the verb itself are considered
(see \citealt[52]{XiaoMcEnery2004} for more details).
This does not rule out the fact that the same verb may express different aspectual properties in other contexts,
but its verb class remains the same,
as the aspectual change can be attributable to other components at the sentential level.
Section 2.3.2 is concerned with the interaction of the reduplication with verb classes,
while the Section 2.3.3 discusses the interaction with viewpoint aspect markers.
The combination with other sentential components such as adjuncts is also discussed in Section 2.3.4.%is briefly touched upon below,
%but a detailed discussion has to be left for future research.

Second, there are more examples.
Regarding volitionality, although (15e) in the previous version of the paper (25c in the current version) is a causative sentence, (13a--b) in the previous version of the paper (17a--b in the current version) are not imperative, conditional or causative (more on this below).
Example (\ref{ex:sheng}) shows the same verb \obj{sheng1} `give birth to' as in (15e) reduplicated in a declarative sentence.
\ea\label{ex:sheng}%我们女人是这么神经质又没用，只能生生孩子，做做女人的活动.。(BCC)
\gll \objex{wo2men} \objex{nv3ren2} \ldots\, \objex{zhi3} \objex{neng2} \obj{sheng1-sheng1} \objex{hai2zi} \ldots \\
we women {} only can give.birth.to-give.birth.to child\\\jambox{(BCC)}
\glt `We women can only give birth to children \ldots'
\z

@@

4) Conjunction reduction. This criterion can only be applied to set apart coordinated phrases from coordinate compound words with a head in common (e.g. 火车 \obj{huo3che1} e 汽车 \obj{qi4che1} in (33) share the head  车 \obj{che1} `vehicle'). But the examples provided by the author(s) to argue against conjunction reduction with reduplicated verbs are completely different: the verbs do not have the head in common (exx. 34). I believe that this is not a reasonable test to argue for the wordhood of reduplicated verbs.

In summary, the tests used to support the morphological status of reduplication appear
unconvincing.

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}\label{morph}
Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
The tests of semantic compositionality and conjunction reduction are deemed unreliable.
\citet[37--38]{Dai1992}, \citeyear[120--122]{Dai1998} explains the problems of conjunction reduction (he calls it ``coordination'').
That leaves us with phrasal extension (or ``modification'' according to \citealt[32]{Dai1992}, \citeyear[117]{Dai1998})
and phrasal substitution (or ``expansion'' according to \citealt[33]{Dai1992}, \citeyear[117--120]{Dai1998}).
These tests requires further clarifications.

First, the modification test suggests that subparts of a word cannot be modified at a phrasal level.
This is possible for a VP (\ref{ex:modVP}), as the NP inside of the VP can be modified by e.g.\ an AP.
\ea\label{ex:modVP} %开红色的门
\gll \objex{kai1} \objex{hong2se4de} \objex{men2}\\
open  red door\\
\glt `open the red door'
\z
In contrast, the individual verbs in reduplication cannot be modified by an e.g.\ AdvP.
(\ref{ex:modVV}) is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
This shows that it has nothing to do with the relative position of the verb and the AdvP.
\ea[*]{\label{ex:modVV} %看偷偷地看
\gll \objex{kan4} \objex{tou1tou1de} \objex{kan4}\\
look secretly look\\
}
\z

@@

%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
Since the reviewer deemed it irrelevant, the section concerning \citet{Ghomeshietal2004} is removed.

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%% YL
\item p. 26, lines 24--25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between. \etag indicates an underspecified list which could be empty or not''. However, it is not entirely clear what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements. This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.

%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
\obj{le} `\textsc{pfv}' marks the perfective aspect.
The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in Section 2.3.3 concerning the semantics of the reduplication and the aspect markers.

@@

Synchronically, A-\obj{yi}-A has the same meaning as AA and both do not refer to the actual number of the event denoted by the verb.
This means that \obj{yi1} `one' in A-\obj{yi}-A does not contribute any specific meaning to the structure
and is only there as a historical remnant.
In this sense,  \obj{yi1} `one' appearing in between the reduplication is synchronically arbitrary. %similar to linking elements in compounds

Besides the obvious conceptual reason that  \obj{yi1} `one' is taken to mean `little/few',
there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.
In Chinese, one form of intensifying reduplication is A-\obj{li}-AB e.g. \obj{hu2-li-hu2tu2} `confused-li-confused',
where the \obj{li} is fixed and also does not bear any meaning.
\citet[137]{Sui2018} assumes that this syllable is filled with \obj{li} because the open syllable \obj{li} is a relatively unmarked phonological constituent \citep{Yip1992}
and the second syllable in A-\obj{li}-AB occupies an unstressed position.
We can see the similarities between \obj{li} in A-\obj{li}-AB and \obj{yi} in A-\obj{yi}-A: they are both relatively unmarked and occupies an unstressed position.
This can also make it easier for  \obj{yi1} `one' rather than other numerals to become part of a fixed structure.
But a phonological account is out of the scope of this paper and has to be left for further research.

### 2024-09-09 chapters/ch02-Phenomenon.tex
add tones, fix typos, add a footnote based on reviewer replies

 \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compared the AA, ABAB and AABB forms of reduplication 
and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identified that AA and ABAB have a diminishing meaning, 
namely that the event happens for a short duration or to a small extent. 
By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress. 
\citet[Sec. 3.1]{Xie2020} also found that AA and ABAB have relatively high productivity, 
whereas the productivity of AABB is low. 
She further showed that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
\citet[277]{Fan1964} proposed that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
while AABB developed from the reiterative rhetoric from Old Chinese. 
These differences seem to suggest that there is a fundmental difference between these two groups of verbal reduplication. 
The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
AA-\textit{kan}, A-\textit{kan}-\textit{kan}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}\textit{yi}\hyp{}A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.

@@

Secondly, \citet[319]{SuiHu2016} show that the reduplication cannot co-occur with a duration or frequency phrase (\ref{ex:durfreq}).
\ea\label{ex:durfreq}
\ea[]{\gll \objex{zhe4} \objex{ge4} \objex{wen4ti2} \objex{da4jia1} \objex{hai2} \objex{yao4} \objex{tao3lun4} \objex{yi2} \objex{hui4er}/\objex{ji3} \objex{ci4}.\\
this \textsc{clf} question everybody still need.to discuss one while/several time\\
\glt `As for this question, everybody still needs to discuss it for a while/several times.'}

@@

The reduplication has a \textit{delimitativeness} meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \citeauthor{Smith1991} (\citeyear[356]{Smith1991}; \citeyear[199--120]{Smith1994}), \citet[14]{Li1996} and \citet[290--291]{Tsao2001} suggest that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet[276]{Fan1964}, \citet[15]{Li1996} and \citet[1]{Qian2000} as the meaning of reduplication as well.
 \citet[276]{Fan1964} further proposes a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet[Sec. 3.1.3]{Zhu1998} suggests that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

As for A-\textit{yi}-A, \citet[273]{Fan1964} compares examples found in novels and plays and concludes that A-\textit{yi}-A has exactly the same meaning as its AA counterpart.
She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
\citet[Sec. 5]{Xing2000} considers that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
The former conveys a casual attitude whereas the latter sounds more serious.%\footnote{This can be a register effect. Register project sponsorship xxxxxxx}
However, he stressed that there is no difference in the delimitative semantics of both forms,
and that the variance in meaning is a pragmatic one.
The difference is also not absolute and often only shows a tendency.
\citet{Xu2002} finds out that compared to A-\textit{yi}-A, one tends to use AA in contexts with strong emotional attitudes, urgent, casual, timid or uncertain contexts.
But he also states that these differences are pragmatic rather than semantic, 
as he argues that AA and A-\textit{yi}-A can be used interchangeably in most cases,
and the specific differences in meaning only arise from specific contexts as a whole.
\citet[15]{Yang2003} suggests that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
We assume A-\textit{yi}-A to be a form of reduplication and that it has the same core semantics as AA.

@@

It is true that  the reduplication of stative and achievement verbs is not as easily acceptable as that of activities and semelfactives.
\citep[155]{XiaoMcEnery2004} classify \obj{bing4} `be sick' as a stative verb.
Indeed, compared  to the questionable reduplication of \obj{bing4} `be sick' in (\ref{ex:redup-stat}),  
 the reduplication of the activity verb \textit{kan} `watch' in (\ref{ex:redup-actV})
and that of the semelfactive verb \textit{kesou} `cough' in (\ref{ex:redup-semel}) are readily acceptable.

@@

On the other hand, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
and indeed \citet[669--670]{Tham2013} herself noted,
verbs expressing psychological states such as these can have a COS interpretation (but not necessarily),
let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
    Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
    and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013},
    these predicates are not included in our examples.}
The following examples contain the reduplication of \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene'.
\ea\label{ex:xiang}%范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
Context: \objex{Wang2} \objex{Sheng4di2} is the actor of the character \objex{Gu4} \objex{Miao3} in a TV series.
\objex{Wang2} Ān\objex{yu3} is another actor in the series.\\
\\
\gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}. \objex{Wang2} Ān\objex{yu3} \objex{ni3} \objex{kuai4dian3} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
\glt `Wang Shengdi \ldots\,  really looks like Gu Miao. Wang Anyu, you too should just look like (your character) already!'

@@

However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat5}) can be found.
Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' are reduplicated.

@@

%\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
%\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}
%\begin{sloppypar}
\ea
\ea\label{ex:redup-achi-stat1}
\gll \objex{deng3} \objex{ren2-men} ba \objex{zhe4} \objex{jian4} \objex{shi4} \obj{wang4}-\obj{wang} \objex{zai4} \objex{shuo1} ba.\footnotemark\\
wait people-\textsc{pl} \textsc{ba} this \textsc{clf} incident forget-forget then talk \textsc{ptc}\\
\glt `Let's wait until people forget this incident a little bit and then talk about it.'\\
\footnotetext{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
%\ex\label{ex:redup-achi-stat2}
%\gll huitou mo ge zao \textit{shutan}-\textit{shutan} ba.\footnotemark\\
%later wipe \textsc{clf} bath be.comfortable-be.comfortable \textsc{ptc}\\
%\glt `Let's take a bath later and be comfortable for a little while.'\\

@@

\ex[*]{\label{ex:teloc}%到附近市场买买东西两天
    \gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi} \objex{liang3} \objex{tian1}.\\
    arrive nearby market buy-buy thing two day\\
    \glt Intended: `(We) went to the market nearby to buy some things for two days.'}
\z\z
The following continuation that cancels the \textit{telo} is also infelicitous (\ref{ex:telod}).
\ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
\gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}, \# \objex{dan4} \objex{shen2me} \objex{ye3} \objex{mei2} \objex{mai3-dao4}.\\
arrive nearby market buy-buy thing {} but anything also not buy-arrive\\
\glt Intended: `(We) went to the market nearby to buy some things, but we didn't buy anything.'
\z
These tests suggest that the reduplicated verbs are indeed achievements,
rather than being used as activities.

@@

As mentioned in \sectref{sec:forms}, the reduplication can only be marked by the perfective aspect marker \textit{le} but not other aspect markers.\footnote{
There is no consensus on which elements exactly are considered aspect markers in Mandarin Chinese. 
We only discuss the most commonly recognized ones here.
}
We believe this incompatibility to be for semantic reasons.

@@

The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981}, \citet[Sec. 4.1]{Dai1992} and \citet[4--5]{Liao2014} list reduplication under morphological processes. 
By contrast, \citet[23]{Arcodiaetal2014}, \citet{Xiong2016}, \citet[146]{BascianoMelloni2017}, \citet[229--231]{YangWei2017}, \citet[330]{MelloniBasciano2018} and \citet{Xie2020}  claim it to be syntactic.
%And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
This section reviews the arguments in \citet{Xie2020},
and applies tests from \citeauthor{Dai1992} (\citeyear[Sec. 7]{Dai1992}, \citeyear[Sec. 2.3--2.4]{Dai1998}) to distinguish words from phrases in Mandarin Chinese.
 %applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
%and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
%(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
The results argue for a morphological analysis of reduplication.

@@

  \ex \gll \objex{jin4-chu1} $\rightarrow$ \obj{jin4}-\obj{jin4}-\obj{chu1}-\obj1{chu}\\
  enter-exit {} enter-enter-exit-exit\\ \jambox{\citep[88]{Xie2020}}
  \glt `enter and exit' `enter and exit repeatedly'

@@

However, a morphological process can be productive, and it does not necessarily change the category or valency of the input.
For instance, the \obj{-able} derivation in English is a productive morphological process.
Tense inflections in English such as \obj{-ed} change neither the category nor the valency of the input verb.
%the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
%The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
%And inflections of tense in German do not change the valency of the input verb.
Further, if \obj{le} is considered to be a morphological element (e.g. \citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \obj{le} does not have to be viewed as a syntactic
process either.
It seems that \citet{Xie2020} only shows that AA and ABAB are different processes than AABB, but not necessarily that the former is syntactic while the latter morphological.

>>>>

 \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compare the AA, ABAB and AABB forms of reduplication 
and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identify that AA and ABAB have a diminishing meaning, 
namely that the event happens for a short duration or to a small extent. 
By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress. 
\citet[Sec. 3.1]{Xie2020} also finds that AA and ABAB have relatively high productivity, 
whereas the productivity of AABB is low. 
She further shows that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
\citet[277]{Fan1964} proposes that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
while AABB developed from the reiterative rhetoric from Old Chinese. 
These differences seem to suggest that there is a fundmental difference between these two groups of verbal reduplication. 
The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
AA-\obj{kan4}, A-\obj{kan4}-\obj{kan4}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}\textit{yi}\hyp{}A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.

@@

Secondly, \citet[319]{SuiHu2016} show that the reduplication cannot co-occur with a duration or a frequency phrase (\ref{ex:durfreq}).
\ea\label{ex:durfreq}
\ea[]{\gll \objex{zhe4} \objex{ge4} \objex{wen4ti2} \objex{da4jia1} \objex{hai2} \objex{yao4} \objex{tao3lun4} \objex{yi2} \objex{hui4er}/\objex{ji3} \objex{ci4}.\\
this \textsc{clf} question everybody still need.to discuss one while/several time\\
\glt `As for this question, everybody still needs to discuss it for a while/several times.'}

@@

The reduplication has a \textit{delimitativeness} meaning (e.g.\ \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \citeauthor{Smith1991} (\citeyear[356]{Smith1991}; \citeyear[199--120]{Smith1994}), \citet[14]{Li1996} and \citet[290--291]{Tsao2001} suggest that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet[276]{Fan1964}, \citet[15]{Li1996} and \citet[1]{Qian2000} as the meaning of reduplication as well.
 \citet[276]{Fan1964} further proposes a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet[Sec. 3.1.3]{Zhu1998} suggests that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

As for A-\textit{yi}-A, \citet[273]{Fan1964} compares examples found in novels and plays and concludes that A-\textit{yi}-A has exactly the same meaning as its AA counterpart.
She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
\citet[Sec. 5]{Xing2000} considers that the major  difference  between AA and A-\textit{yi}-A lies in the speaker's attitude.
The former conveys a casual attitude whereas the latter sounds more serious. %\footnote{This can be a register effect. Register project sponsorship xxxxxxx}
However, he stresses that there is no difference in the delimitative semantics of both forms,
and that the variance in meaning is a pragmatic one.
The difference is also not absolute and often only shows a tendency.
\citet{Xu2002} finds out that compared to A-\textit{yi}-A, one tends to use AA in contexts with strong emotional attitudes, urgent, casual, timid or uncertain contexts.
But he also states that these differences are pragmatic rather than semantic, 
as he argues that AA and A-\textit{yi}-A can be used interchangeably in most cases,
and the differences in meaning only arise from specific contexts as a whole.
\citet[15]{Yang2003} suggests that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
We assume A-\textit{yi}-A to be a form of reduplication and that it has the same core semantics as AA.

@@

It is true that  the reduplication of stative and achievement verbs is not as easily acceptable as that of activities and semelfactives.
\citet[155]{XiaoMcEnery2004} classify \obj{bing4} `be sick' as a stative verb.
Indeed, compared  to the questionable reduplication of \obj{bing4} `be sick' in (\ref{ex:redup-stat}),  
 the reduplication of the activity verb \obj{kan4} `watch' in (\ref{ex:redup-actV})
and that of the semelfactive verb \obj{ke2sou4} `cough' in (\ref{ex:redup-semel}) are readily acceptable.

@@

On the other hand, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
and indeed \citet[669--670]{Tham2013} herself noted,
verbs expressing psychological states such as these can have a COS interpretation (but not necessarily),
let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
    Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g.\ \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
    and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013},
    these predicates are not included in our examples.}
The following examples contain the reduplication of \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene'.
\ea\label{ex:xiang}%范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
Context: \objex{Wang2} \objex{Sheng4di2} is the actor of the character \objex{Gu4} \objex{Miao3} in a TV series.
\objex{Wang2} Ān\objex{yu3} is another actor in the series.\\
\\
\gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}. \objex{Wang2} Ān\objex{yu3} \objex{ni3} \objex{kuai4dian3} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
\glt `Wang Shengdi \ldots\,  really looks like Gu Miao. Wang Anyu, you too should just look like (your character) already!'

@@

However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat5}) can be found.
Here, achievement verbs like \obj{wang4} `forget' and \obj{sheng1} `give birth to' are reduplicated.

@@

%\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
%\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}
%\begin{sloppypar}
\ea
\ea\label{ex:redup-achi-stat1}
\gll \objex{deng3} \objex{ren2-men} ba \objex{zhe4} \objex{jian4} \objex{shi4} \obj{wang4}-\obj{wang} \objex{zai4} \objex{shuo1} ba.\footnotemark\\
wait people-\textsc{pl} \textsc{ba} this \textsc{clf} incident forget-forget then talk \textsc{ptc}\\
\glt `Let's wait until people forget this incident a little bit and then talk about it.'\\
\footnotetext{\objex{Liu2}, \objex{Zhen1}. 1963. \obj{Chang2} \obj{chang2} \obj{de} \obj{liu2shui3} \textit{[Long long water]}, 72. Beijing: The Writers Publishing House.}
%\ex\label{ex:redup-achi-stat2}
%\gll huitou mo ge zao \textit{shutan}-\textit{shutan} ba.\footnotemark\\
%later wipe \textsc{clf} bath be.comfortable-be.comfortable \textsc{ptc}\\
%\glt `Let's take a bath later and be comfortable for a little while.'\\

@@

\ex[*]{\label{ex:teloc}%到附近市场买买东西两天
    \gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi} \objex{liang3} \objex{tian1}.\\
    arrive nearby market buy-buy thing two day\\
    \glt Intended: `(We) went to the market nearby to buy some things for two days.'}
\z\z
The following continuation that cancels the \textit{telos} is also infelicitous (\ref{ex:telod}).
\ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
\gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}, \# \objex{dan4} \objex{shen2me} \objex{ye3} \objex{mei2} \objex{mai3-dao4}.\\
arrive nearby market buy-buy thing {} but anything also not buy-arrive\\
\glt Intended: `(We) went to the market nearby to buy some things, but we didn't buy anything.'
\z
These tests suggest that the reduplicated verbs are indeed achievements,
rather than being used as activities.

@@

As mentioned in \sectref{sec:syn-dis}, the reduplication can only be marked by the perfective aspect marker \textit{le} but not other aspect markers.\footnote{
There is no consensus on which elements exactly are considered aspect markers in Mandarin Chinese. 
We only discuss the most commonly recognized ones here.
}
We believe this incompatibility to be for semantic reasons.

@@

The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981}, \citet[Sec. 4.1]{Dai1992} and \citet[4--5]{Liao2014} list reduplication under morphological processes. 
By contrast, \citet[23]{Arcodiaetal2014}, \citet{Xiong2016}, \citet[146]{BascianoMelloni2017}, \citet[229--231]{YangWei2017}, \citet[330]{MelloniBasciano2018} and \citet{Xie2020}  claim it to be syntactic.
%And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
This section reviews the arguments in \citet{Xie2020},
and applies tests from \citeauthor{Dai1992} (\citeyear[Sec. 7]{Dai1992}, \citeyear[Sec. 2.3--2.4]{Dai1998}) to distinguish words from phrases in Mandarin Chinese.
 %applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
%and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
%(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
The results are compatible with a lexical analysis.

@@

  \ex \gll \objex{jin4-chu1} $\rightarrow$ \obj{jin4}-\obj{jin4}-\obj{chu1}-\obj{chu1}\\
  enter-exit {} enter-enter-exit-exit\\ \jambox{\citep[88]{Xie2020}}
  \glt `enter and exit' `enter and exit repeatedly'

@@

However, a morphological process can be productive, and it does not necessarily change the category or valency of the input.
For instance, the \obj{-able} derivation in English is a productive morphological process.
Tense inflections in English such as \obj{-ed} change neither the category nor the valency of the input verb.
%the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
%The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
%And inflections of tense in German do not change the valency of the input verb.
Further, if \obj{le} is considered to be a morphological element (e.g.\ \citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \obj{le} does not have to be viewed as a syntactic
process either.
It seems that \citet{Xie2020} only shows that AA and ABAB are different processes than AABB, but not necessarily that the former is syntactic while the latter morphological.
